\chapter{Background}

% TODO: Maybe something about assumed knowledge

% TODO: Maybe a notation section
Notation: we write $1$ for the neutral element of a group.

\section{Coxeter Groups}

\begin{definition}
    A \textit{Coxeter system} $(W,S)$ is a group $W$ and a finite subset $S = \{s_1, ..., s_n\} \subset W$ under the following conditions. For any $s,t \in S$, $(st)^{m_{st}} = 1$ where $m_{st} \in \Z_{>0}\cup\{\infty\}$ such that  $m_{st} = 1$ if $s = t$, and $m_{st} = m_{ts} \in \{2,3,...\} \cup \{\infty\}$ if $s \neq t$. In other words, $W = \angl{s \in S \mathrel{|} (st)^{m_{st}} = 1}$ with generator $S$. We call $W$ a \textit{Coxeter group}.
\end{definition}

The value $m_{st} = \infty$ indicates there are no relations of the form $(st)^{m} = 1$ for any $m \in \Z_{>0}$. We often call relations of the form $s^2 = 1$ \textit{quadratic relations}. The quadratic relations on the generators of the Coxeter group imply that $s^{-1} = s$ and $(st)^{-1} = t^{-1} s^{-1} = ts$. Moreover, if $s \neq t$ and $m_{st} < \infty$, then we can use the quadratic relations to write $(st)^{m_{st}} = 1$ equivalently as
\[
    \underbrace{sts...}_{m_{st}} = \underbrace{tst...}_{m_{st}},
\]
which we call \textit{braid relations}.
% TODO: Add reference to why they are called braid relations
Coxeter systems are closely related to reflections, so we often call elements of $S$ \textit{simple reflections}, and elements in $W$ that are conjugates to elements in S \textit{reflections}.
% TODO: Add reference to why they are reflections (ch2, or of it is added to this paper)

\n\begin{example}\label{example-CG}
    The permutation group of $n$ elements $S_n$ is a Coxeter group generated by the set of transpositions $S = \{(i,i+1) \in S_n : 1 \leq i \leq n-1\}$. Let $s_i := (i,i+1)$. We know from algebra that $S$ generates $S_n$, so let us check the relations.
    \begin{itemize}
        \item For any $i$, $s_i^2 = (i,i+1)(i,i+1) = 1$.
        \item For $i > j+1$, the transpositions $(i,i+1)$ and $(j,j+1)$ are disjoint so $(s_i s_j)^2 = (i,i+1)(j,j+1)(i,i+1)(j,j+1) = 1$.
        \item For $i = j+1$, $(s_i s_j)^3 = ((i,i+1)(j,j+1))^3 = (i,i+1,i+2)^3 = 1$.
    \end{itemize}
    These are sometimes called the Coxeter system of type $A_{n-1}$, for $n \geq 2$.

    \n
    An easy case is the Coxeter group $W \simeq S_3$ with generators $S = \{s,t\}$ where $s,t$ correspond to transpositions $(12)$ and $(23)$ respectively. By the quadratic and braid relations, we find that the elements of $W$ are exactly $1,s,t,st,ts,sts=tst$. We will frequently revisit this example. % REVIEW: Rewrite this last sentence after I have used it more

    % TODO: Should I add more details?
\end{example}

\begin{definition}
    Let $w \in W$. As $S$ generates $W$, we can write $w = s_1 s_2 ... s_k$ for some $s_1,...,s_k \in S$. We say the sequence $(s_1, ..., s_k)$ is an \textit{expression} for $w$ of \textit{length} $k$. Given the relations in the definition, $w \in W$ is not uniquely expressed as such a sequence, so we write $\ul{w}$ to denote a choice of expression $(s_1, ..., s_k)$ for $w$.
\end{definition}

\begin{definition}
    Let $w \in W$. For any expression $\underline{w} = (s_1, ..., s_k)$, we say the \textit{length of $\underline{w}$} is $k$, and write $\ell(\ul{w}) = k$. The \textit{length of $w$}, written $\ell(w)$ is the smallest integer $k$ such that $w$ admits an expression of length $k$. We say an expression $\ul{w}$ is \textit{reduced} if $\ell(\ul{w}) = \ell(w)$.
\end{definition}

Note that $\ell(w) = 0$ if and only if $w = 1$.

\n
The following are results regarding reduced expressions.

\begin{theorem}[Exchange condition]
    Let $\underline{w} = (s_1, ..., s_k)$ be a reduced expression for $w \in W$, and let $t \in S$. If $\ell(wt) < \ell(w)$, then there exists an integer $i \in \{1,2,...,k\}$ such that $wt = s_1 ... \hat{s_i} ... s_k$, i.e. with $s_i$ omitted.
\end{theorem}

% TODO: Proof?
% TODO: Example?

\begin{corollary}[Deletion Condition]
    Let $\underline{w} = (s_1, ..., s_k)$ be an expression for $w \in W$ where $\ell(w) < k$, i.e. not a reduced expression. Then there exists some $i < j$ such that $w = s_1 ... \hat{s_i} ... \hat{s_j} ... s_k$.
\end{corollary}

In other words, if an expression is not reduced, two elements in the expression may be cancelled to result in a shorter expression.

% TODO: Proof?
% TODO: Example?

\begin{theorem}[Matsumoto, 1964]\label{thm-matsumoto}
    Any two reduced expressions for $w \in W$ are related by braid relations.
\end{theorem}

% TODO: Put a proof, or reference to one

We can also define a partial order on $W$.
% TODO: What is this used for?

\begin{definition}[Bruhat Order]
    Let $T$ be the set of elements of $W$ that are conjugate to elements in $S$. Define a partial order $\leq$ on $W$ such that for $x,y \in W$, $x \leq y$ if and only if there exists a chain $x=x_0,x_1,...,x_m=y$ of elements in $W$ such that $\ell(x_i) < \ell(x_{i+1})$ and $x_i^{-1} x_{i+1} \in T$ for each $i = 0,1,...,m-1$.
\end{definition}

That is $x_{i+1}$ is $x_i$ multiplied on the right with a conjugate of an element in $S$ such that its length is longer than $x_i$. Note that we can equivalently multiply on the left because for any $t \in T$ we can write $xt = (xtx^{-1})x$ where $xtx^{-1} \in T$.

% TODO: Explain why we need T

\n
Equivalently let $y = s_1 ... s_k$ be a reduced expression, and we can define $x \leq y$ to be if and only if there exists a reduced expression $x = s_{i_1} ... s_{i_\ell}$ such that $1 \leq i_1 < ... < i_\ell \leq k$. In other words, $x$ is $y$ after removing some terms from a reduced expression (we say $x$ is a \textit{subexpression} of $y$).

% TODO: Why is it equivalent? (Exercise 1.64)

\begin{example}
    The Hasse diagram for the Bruhat order on $S_3$ is as follows (using the labelling of elements from Example \ref{example-CG}).
    \begin{center}
        \begin{tikzpicture}
            \node (1) at (0,0) {$1$};
            \node (s) at (-1.5,1.5) {$s$};
            \node (t) at (1.5,1.5) {$t$};
            \node (st) at (-1.5,3) {$st$};
            \node (ts) at (1.5,3) {$ts$};
            \node (sts) at (0,4.5) {$sts=tst$};

            \draw (1)--(s);
            \draw (1)--(t);
            \draw (s)--(st);
            \draw (t)--(st);
            \draw (s)--(ts);
            \draw (t)--(ts);
            \draw (st)--(sts);
            \draw (ts)--(sts);
        \end{tikzpicture}
    \end{center}
\end{example}


We will work with the geometric representation of Coxeter systems.

\begin{definition}
    Given a Coxeter system $(W,S)$, define a representation $V$ of $W$ as follows. Let $V$ be a vector space over $\R$ with basis elements $\{\alpha_s : s \in S\}$. Equip $V$ with a symmetric bilinear form $(-,-)$ defined by
    \[
        (\alpha_s, \alpha_t) = - \cos \frac{\pi}{m_{st}}.
    \]
    If $m_{st} = \infty$ we define $\pi/m_{st} = 0$. Define the $W$-action on $V$ such that for $s \in S$ and $v \in V$,
    \[
        s \cdot v = v - 2(v,\alpha_s) \alpha_s.
    \]
    We call this the \textit{geometric representation} of the Coxeter system.
\end{definition}

Note that this is defined for both finite and infinite Coxeter groups.

\begin{proposition}
    For any Coxeter system, the geometric representation is faithful.
\end{proposition}

% TODO: Proof?

\section{Hecke Algebra}

% TODO: Introduction/motivation

Let $\Z[v, v^{-1}]$ be the set of integer Laurent polynomials, for an indeterminate $v$.

\begin{definition}
    The \textit{Hecke algebra} $\mcal{H}$ for a Coxeter system $(W,S)$ is the unital associative algebra over $\Z[v,v^{-1}]$ generated by $\{\delta_s : s \in S\}$ with the following relations.
    \begin{itemize}
        \item $\delta_s^2 = (v^{-1} - v)\delta_s + 1$, for any $s \in S$.
        \item $\underbrace{\delta_s \delta_t \delta_s...}_{m_{st}} = \underbrace{\delta_t \delta_s \delta_t...}_{m_{st}}$, for any $s,t \in S$ where $m_{st} < \infty$.
    \end{itemize}
\end{definition}

Recall that an algebra over a commutative ring $R$ is an $R$-module with an $R$-bilinear multiplication operation. A unital associative algebra over $R$ is then an algebra over $R$ for which multiplication is associative and has a multiplicative identity.

\n
Similarly to Coxeter groups, we call the first relations \textit{quadratic relations} and the second \textit{braid relations}.

% TODO: Why is the quadratic relation is the way it is

\n
Note that the quadratic relation is equivalent to $(\delta_s - v^{-1})(\delta_s + v) = 0$.

% TODO: Why? Why is this important?


% REVIEW: Add more on how it relates to coxeter groups
% \begin{remark}
%     If $A$ is a commutative ring, then a ring homomorphism $\phi: \Z[v ,v^{-1}] \to A$ gives $A$ the structure of a $\Z[v,v^{-1}]$-algebra.
%     % (TODO: so that the action of $x \in \Z[v,v^{-1}]$ on $a \in A$ is $x \cdot a = \phi(x) a$??).
%     With this we can form the specialisation $\mcal{H}_\phi := A \otimes_{\Z[v,v^{-1}]} \mcal{H}$ of $\mcal{H}$.
%     % (Look more into what specialisation is and does.)
%     Note that this specialisation is uniquely determined by the ring $A$ and the invertible element $\phi(v) \in A^\times$.
%     In particular if $A = \Z$ and $\phi(v) = 1$, the specialisation of $\mathrm{H}$ is isomorphic to the group algebra $\Z[W]$ (mapping $\delta_s$ to $s \in S$). Because of this, the Hecke algebra is a \textit{deformation} of the group algebra of $W$. Also notice that in the specialisation $v \mapsto 1$, the quadratic relation of the Hecke algebra becomes the quadratic relation of the Coxeter group.
%     % TODO: What does this say about Hecke algebra and coxeter groups?
% \end{remark}

For $w \in W$ with reduced expression $w = s_1 s_2 ... s_k$, define the element $\delta_w = \delta_{s_1}  \delta_{s_2} ... \delta_{s_k}$ of $\mcal{H}$. Since $\mcal{H}$ has braid relations identical to $W$, Matsumoto's theorem (Theorem \ref{thm-matsumoto}) implies that this is independent of the choice of reduced expression. Note that we set $\delta_1 = 1$


\begin{theorem}
    The Hecke algebra is a free $\Z[v,v^{-1}]$-module with basis $\{\delta_w : w \in W\}$.
\end{theorem}

\begin{definition}
    We call $\{\delta_w : w \in W\}$ the \textit{standard basis} of $\mcal{H}$.
\end{definition}


\begin{proposition}
    The following multiplication formulae hold in $\mcal{H}$. For $w \in W$ and $s \in S$,
    \[
        \delta_w \delta_s =
        \begin{cases}
            \delta_{ws}                        & \text{if } ws > w, \\
            (v^{-1} - v)\delta_w + \delta_{ws} & \text{if } ws < w, \\
        \end{cases}
    \]
    and
    \[
        \delta_s \delta_w =
        \begin{cases}
            \delta_{sw}                        & \text{if } ws > w, \\
            (v^{-1} - v)\delta_w + \delta_{sw} & \text{if } ws < w. \\
        \end{cases}
    \]
\end{proposition}

\begin{proposition}
    For any simple reflection $s \in S$,
    \[
        \delta_s^{-1} = \delta_s + (v - v^{-1}).
    \]
\end{proposition}
This follows from the quadratic relation in $\mcal{H}$.

\n

\begin{proposition}
    Since the generators $\{\delta_s : s \in S\}$ of $\mcal{H}$ are invertible, $\delta_w$ is invertible for every $w \in W$. Moreover,
    \[
        \delta_{w^{-1}}^{-1} = \delta_w + \sum_{x < w} a_x \delta_x
    \]
    for some $a_x \in \Z[v,v^{-1}]$.
\end{proposition}

\n\grey{Kazhdan-Lusztig Basis}

There is another basis known as the Kazhdan-Lusztig basis.

\begin{definition}
    The \textit{Kazhdan-Lusztig involution} or \textit{bar involution} is a $\Z$-linear involution $\mcal{H} \to \mcal{H}, h \mapsto \ol{h}$ defined on generators $\ol{v} = v^{-1}$ and $\ol{\delta_s} = \delta_s^{-1}$ for $s \in S$, such that it distributes across products as a ring automorphism.
\end{definition}

% REVIEW: CHeck if we need: \ol{\deta_w} = \delta_{w^{-1}}^{-1}

\begin{definition}
    The \textit{Kazhdan-Lusztig basis} for $\mcal{H}$ is the set $\{b_w : w \in W\} \subseteq \mcal{H}$ such that for any $w \in W$,
    \begin{itemize}
        \item $b_x$ is self-dual, i.e. $\ol{b_x} = b_x$, and
        \item $b_x$ has the form
              \[
                  b_x = \delta_x + \sum_{y<x} h_{y,x} \delta_y
              \]
              for some $h_{y,x} \in v\Z[v]$, where $<$ is the Bruhat order.
    \end{itemize}
    The coefficients $h_{y,x} \in v\Z[v]$ are called \textit{Kazhdan-Lusztig polynomials}.
\end{definition}

Additionally, we set $h_{x,x} = 1$ and $h_{y,x} = 0$ if $y \not\leq x$ in the Bruhat order. The second condition is sometimes called the \textit{degree bound} condition.

\begin{lemma}
    The Kazhdan-Lusztig basis is unique.
\end{lemma}

\n\grey{Standard Form}

\n\grey{Construction of Kazhdan-Lusztig basis}
% Do we need this?
% TODO: Will probably need introduction of coxter complexes to have a diagram to do examples

\n\grey{Category Theory}

\n\grey{Soergel Bimodules}
